landlord

### 2023-05-10 src/landlord.Rmd
cleaning up landlord code and output results into excel

library(googlesheets4)
library(janitor)
library(tidyverse)
library(kableExtra)
library(DT)

@@

# select_MSAs <- read_sheet("https://docs.google.com/spreadsheets/d/1lmTpSDwVANxdAg5sW87Q8l_gtig7M0EjPPJ6J5_7dwg/edit?usp=sharing")
```

```{r}
#filter by new MSA list
# new_MSA_list <- unique(select_MSAs$cbsa)
# 
# MSA_landlord_data <- MSA_landlord_data %>% 
#   filter(cbsa %in% c(new_MSA_list))
```

```{r}
#security_deposit_limit
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    security_depopsit_limit_num = case_when(
      security_deposit_limit == "N" ~ 1.0, 
      security_deposit_limit == "1_month_rent" ~ 0.0,
      security_deposit_limit == "2_months_rent" ~ 0.5))

# #notice_of_entry_days
# MSA_landlord_data <- MSA_landlord_data %>% 
#   mutate(
#     notice_for_entry_days_num = case_when(
#       notice_for_entry_days == "N" ~ 1.0, 
#       notice_for_entry_days == "0" ~ 1.0,
#       notice_for_entry_days == "0.5" ~ 0.75,
#       notice_for_entry_days == "1" ~ 0.5,
#       notice_for_entry_days == "2" ~ 0.0,))
```

```{r}
#normalize eviction notice (days)
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    eviction_notice_days_normalized = (eviction_notice_days-min(eviction_notice_days))/(max(eviction_notice_days)-min(eviction_notice_days)) 
  )

#"invert" normalized score for eviction notice days
#1 - normalized score (since more eviction notice is worse for landlords)
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    eviction_notice_days_normalized_inverted = 1 - eviction_notice_days_normalized
  )
```

```{r}
#calculate landlord category score

@@

datatable(MSA_landlord_data, extensions = 'Buttons', options = list(
    dom = 'Bfrtip',
    buttons = c('copy', 'csv', 'excel', 'pdf', 'print')
  )
)
```

>>>>

library(googlesheets4)
library(janitor)
library(tidyverse)
library(kableExtra)
library(DT)
library(ggplot2)
library(readxl)
library(here)
source(here("R/normalize.R"))

@@

```

```{r}
#security_deposit_limit
MSA_landlord_data <- MSA_landlord_data %>% 
  mutate(
    security_deposit_limit_num = case_when(
      security_deposit_limit == "N" ~ 1.0, 
      security_deposit_limit == "1_month_rent" ~ 0.0,
      security_deposit_limit == "2_months_rent" ~ 0.5)) %>% 
    #"invert" normalized score for eviction notice days
#1 - normalized score (since more eviction notice is worse for landlords)
  mutate(n_eviction_notice = 1- normalize(eviction_notice_days))

# assign numeric values to security deposit limit for all states
state_landlord_policy <- state_landlord_policy %>% 
  mutate(security_deposit_limit = case_when(
      deposit_limit == "N" ~ 1.0, 
      deposit_limit == "1_months_rent" ~ 0.0,
      deposit_limit == "1_month_rent" ~ 0.0,
      deposit_limit == "1.5_months_rent" ~ 0.25,
      deposit_limit == "2_months_rent" ~ 0.5,
      deposit_limit == "2.5_months_rent" ~ 0.75,
      deposit_limit == "3_months_rent" ~ 0.75)) %>% 
   #"invert" normalized score for eviction notice days
#1 - normalized score (since more eviction notice is worse for landlords)
  mutate(n_eviction_notice = 1- normalize(eviction_days))

```

#calculate landlord category score

```{r}

@@

```
